Draft-assinment1

### 2017-02-19 Draft-xuezhou-sjb.Rmd
Update Draft-xuezhou-sjb.Rmd
update toc

#Table of Contents
* 1.[Introduction](#Introduction)
* 2.[Goal](#Goal)
* 3.[Dataset Preparation](#dataprep)
* 4.[Objective](#objective)
* 5.[Summary of variables](#variablesummary)
 * 5.1 Individual variable summary
  * 5.1.1 School
    * 5.1.1.1 State
    * 5.1.1.2 Predominant Degree
    * 5.1.1.3 Control of Institution
  * 5.1.2 Student Body
    * 5.1.2.1 [Percentage first-generation students](#5.1.2.1)
    * 5.1.2.2 Number of applications
  * 5.1.3 Cost 
    * 5.1.3.1 [Average net price for Title IV institutions(both public and private institutions)](#5.1.3.1)
    * 5.1.3.2 [Percentage of students who are financially independent](#5.1.3.2)
  * 5.1.4 Financial Aid
    * 5.1.4.1 [Percentage of undergraduates who receive a Pell Grant](#5.1.4.1)
    * 5.1.4.2 [Percent of all federal undergraduate students receiving a federal student loan](#5.1.4.2l)
    * 5.1.4.3 [The median debt for students who have completed](#5.1.4.3)
    * 5.1.4.4 The median debt for students who have not completed
  * 5.1.5 Earning
    * 5.1.5.1 [Median family income in real 2015 dollars](#5.1.5.1)
    * 5.1.5.2 Earning after graduation
  * 5.1.6 Repayment
    * 5.1.6.1 3-year Repayment rate
    * 5.1.6.2 3-year Default rate
* 6.Relationship between variables
 * 6.1 [The relationship between NPT4_COMBINE and State](#6.1)
 * 6.2 [The relationship between Debt and Cost](#6.2)
 * 6.3 [The relationship between Percentage of Pell Grant and college type(CONTROL)](#6.3)
 * 6.4 [The relationship between Percentage first-generation students and States](#6.4)
 * 6.5 [The relationship between family income and percentage of Pell Grant](#6.5)
 * 6.6 [The relationship between DEP_STAT_PCT_IND and Control](#6.6)
 * 6.7 [The relationship between PCTLOAN and Control](#6.7)
 * 6.8 cost and median debts with earning
 * 6.9 default with earning
 * 6.10 degree type vs. earning
 * 6.11 predominant degree, control  and earning after 6 year of entry
 * 6.12 predominant degree + control (count)
 * 6.13 control + earning
 * 7. Findings and Conclusion

@@

###5.1.2 Student Body
####5.1.2.1 Percentage first-generation students
This element identifies the share of federally aided students at the institution who report that they are first generaion on the FAFSA (Free Application for Federal Student Aid). First generation students are defined as sudents in which neither parents completed college.

@@

####5.1.2.2 Number of applications
The variable APPL_SCH_PCT_GE2 is to describe the percentage of students who list two and more than two institutions when he apply for financial aid when apply for universities. This information is only available to students who submit their applications for federal aid, and not cover the whole student body. Nevertheless, this variable still can provides some useful insights about how many universities a student usually apply to.

@@

###5.1.3 Cost
####5.1.3.1 Average net price for Title IV institutions(both public and private institutions)

@@

####5.1.3.2 Percentage of students who are financially independent

@@

###5.1.4 Financial Aid 
####5.1.4.1 Percentage of undergraduates who receive a Pell Grant

@@

####5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan

@@

####5.1.4.3 The median debt for students who have completed

@@

####5.1.5.2 Earning after graduation
We selected two variables MD_EARN_WNE_P6, MD_EARN_WNE_P10 in the earning group to study students' post-graduation earning. MD_EARN_WNE_P6 is the median earning for students six years after their entry, which corresponds to two years after gradutaion. Likewise, MD_EARN_WNE_P10 is the median earning ten years after their entry, which corresponds to four years after graduation. These two metrics give us an idea of how much money students are making after their graduation, in both short and medium terms,

@@

###5.1.6 Repayment 
####5.1.6.1 3-year Repayment rate
The variable RPY_3YR_RT_SUPP measure the percentage of student who entered repayemtn from October 1, 2010 to September 30, 2011, and made progress in the following three years. Repayment rates are generally considered most sensitive than default rates(we study later), which measure only the worse-case scenario for repayment outcomes. From the summary statistics, we see that 50% institutions have 40% of students who are making progress in their repayment. A histogram is also plotted to show the distribution, clearly with a heavy tail.

@@

####5.1.6.2 3-year Default rate
The three-year cohort default rate describe the repayment in the opposite of repayment rate. In this dataset, it was calculated using the cohort of borrowers who entered repayment on their federal student loans between Octorber 1, 2010 to September 30, 2011, and who defaulted before September 2012. The median default rate aross all universities is 13%, which means that 50% of universities have 13 out of 100 students defaulted their loan!

>>>>

#Table of Contents
* 1.[Introduction](#Introduction)
* 2.[Goal](#Goal)
* 3.[Dataset Preparation](#dataprep)
* 4.[Objective](#objective)
* 5.[Summary of variables](#variablesummary)
 * 5.1 [Individual variable summary](#5.1)
  * 5.1.1 [School](#5.1.1)
    * 5.1.1.1 [State](#5.1.1.1)
    * 5.1.1.2 [Predominant Degree](#5.1.1.2)
    * 5.1.1.3 [Control of Institution](#5.1.1.3)
  * 5.1.2 Student Body
    * 5.1.2.1 [Percentage first-generation students](#5.1.2.1)
    * 5.1.2.2 [Number of applications](#5.1.2.2)
  * 5.1.3 Cost 
    * 5.1.3.1 [Average net price for Title IV institutions(both public and private institutions)](#5.1.3.1)
    * 5.1.3.2 [Percentage of students who are financially independent](#5.1.3.2)
  * 5.1.4 Financial Aid
    * 5.1.4.1 [Percentage of undergraduates who receive a Pell Grant](#5.1.4.1)
    * 5.1.4.2 [Percent of all federal undergraduate students receiving a federal student loan](#5.1.4.2l)
    * 5.1.4.3 [The median debt for students who have completed](#5.1.4.3)
    * 5.1.4.4 [The median debt for students who have not completed](#5.1.4.4)
  * 5.1.5 Earning
    * 5.1.5.1 [Median family income in real 2015 dollars](#5.1.5.1)
    * 5.1.5.2 [Earning after graduation](#5.1.5.2)
  * 5.1.6 Repayment
    * 5.1.6.1 [3-year Repayment rate](#5.1.6.1)
    * 5.1.6.2 [3-year Default rate](#5.1.6.2)
* 6.Relationship between variables
 * 6.1 [The relationship between NPT4_COMBINE and State](#6.1)
 * 6.2 [The relationship between Debt and Cost](#6.2)
 * 6.3 [The relationship between Percentage of Pell Grant and college type(CONTROL)](#6.3)
 * 6.4 [The relationship between Percentage first-generation students and States](#6.4)
 * 6.5 [The relationship between family income and percentage of Pell Grant](#6.5)
 * 6.6 [The relationship between DEP_STAT_PCT_IND and Control](#6.6)
 * 6.7 [The relationship between PCTLOAN and Control](#6.7)
 * 6.8 [cost and median debts with earning](#6.8)
 * 6.9 [default with earning](#6.9)
 * 6.10 [degree type vs. earning](#6.10)
 * 6.11 [predominant degree, control  and earning after 6 year of entry](#6.11)
 * 6.12 [predominant degree + control (count)](#6.12)
 * 6.13 [control + earning](#6.13)
* 7. [Findings and Conclusion](#7)

@@

###5.1.2 Student Body
####5.1.2.1 Percentage first-generation students<a id="5.1.2.1"></a>
This element identifies the share of federally aided students at the institution who report that they are first generaion on the FAFSA (Free Application for Federal Student Aid). First generation students are defined as sudents in which neither parents completed college.

@@

####5.1.2.2 Number of applications<a id="5.1.2.2"></a>
The variable APPL_SCH_PCT_GE2 is to describe the percentage of students who list two and more than two institutions when he apply for financial aid when apply for universities. This information is only available to students who submit their applications for federal aid, and not cover the whole student body. Nevertheless, this variable still can provides some useful insights about how many universities a student usually apply to.

@@

###5.1.3 Cost<a id="5.1.3"></a>
####5.1.3.1 Average net price for Title IV institutions(both public and private institutions)<a id="5.1.3.1"></a>

@@

####5.1.3.2 Percentage of students who are financially independent<a id="5.1.3.2"></a>

@@

###5.1.4 Financial Aid 
####5.1.4.1 Percentage of undergraduates who receive a Pell Grant<a id="5.1.4.1"></a>

@@

####5.1.4.2 Percent of all federal undergraduate students receiving a federal student loan<a id="5.1.4.2"></a>

@@

####5.1.4.3 The median debt for students who have completed<a id="5.1.4.3"></a>

@@

####5.1.5.2 Earning after graduation<a id="5.1.5.2"></a>
We selected two variables MD_EARN_WNE_P6, MD_EARN_WNE_P10 in the earning group to study students' post-graduation earning. MD_EARN_WNE_P6 is the median earning for students six years after their entry, which corresponds to two years after gradutaion. Likewise, MD_EARN_WNE_P10 is the median earning ten years after their entry, which corresponds to four years after graduation. These two metrics give us an idea of how much money students are making after their graduation, in both short and medium terms,

@@

###5.1.6 Repayment 
####5.1.6.1 3-year Repayment rate<a id="5.1.6.1"></a>
The variable RPY_3YR_RT_SUPP measure the percentage of student who entered repayemtn from October 1, 2010 to September 30, 2011, and made progress in the following three years. Repayment rates are generally considered most sensitive than default rates(we study later), which measure only the worse-case scenario for repayment outcomes. From the summary statistics, we see that 50% institutions have 40% of students who are making progress in their repayment. A histogram is also plotted to show the distribution, clearly with a heavy tail.

@@

####5.1.6.2 3-year Default rate<a id="5.1.6.2"></a>
The three-year cohort default rate describe the repayment in the opposite of repayment rate. In this dataset, it was calculated using the cohort of borrowers who entered repayment on their federal student loans between Octorber 1, 2010 to September 30, 2011, and who defaulted before September 2012. The median default rate aross all universities is 13%, which means that 50% of universities have 13 out of 100 students defaulted their loan!
